Guide to repository of supplementary resources

### 2023-04-18 index.Rmd
v1.0.0: Paper Publication Release
Update Index files with link to the version 1.0.0

[The repository on github, revision1 branch.](https://github.com/UZH-PEG/diversity_envresp1/tree/main)

[The respository on Zenodo with DOI 10.5281/zenodo.7360272](https://doi.org/10.5281/zenodo.7360272)

>>>>

[The repository on github, current version 1.0.0.](https://github.com/UZH-PEG/diversity_envresp1/releases/tag/v1.0.0)

[The respository on Zenodo with the versioned DOI 10.5281/zenodo.7744094
](https://zenodo.org/record/7744094) - UPDATED
